Global Optimization of the Analogue Method by Means of Genetic Algorithms

### 2015-08-12 Optimization - Journal of Climate/template.tex
Personal corrections.

\abstract{Enter the text of your abstract here.}

@@

\section{Introduction}

The analogue method is a downscaling technique based on the idea expressed by \citet{Lorenz1969}. It aims at forecasting a predictand, often the daily precipitation, on the basis of predictor variables describing the synoptic atmospheric circulation. Its main hypothesis is that similar situations in terms of atmospheric circulation are likely to lead to similar local weather \citep{Bontron2005}.

@@

Multiple variations of the methods are possible, and some aspects and parameters will not be detailed hereafter. There are mainly 2 implementations that are used most often: one that relies on an analogy of the atmospheric circulation, and another that adds a second level of analogy on humidity variables \citep{Obled2002, Bontron2005, Marty2012}.

The method based on the analogy of the synoptic circulation consists in the following steps (Table \ref{table:params_R1}): For a target date, we evaluate the similarity of the atmospheric circulation with every day of the archive by processing the S1 criteria \citep[Eq.\ (\ref{eq:S1}), ][]{Teweles1954, Drosdowsky2003}, which is a comparison of gradients, over a certain spatial window. \citet{Bontron2005} showed that the geopotential heights at 500~hPa and 1000~hPa are the best first predictors of the NCEP/NCAR reanalysis dataset, and that the S1 criteria performs better than scores based on absolute distances. The reason for such better results is that the S1 criteria allows comparing the circulation pattern, by means of the gradients, rather than the absolute value of the geopotential heights. To cope with seasonal effects, candidate data are extracted for every year from the archive within a period of 4 months centred around the target date.

@@

The $N_{1}$ dates with the lowest values of S1 are considered as analogues to the target day. The number of analogues, $N_{1}$, is a parameter to calibrate. It has an optimum clearly identifiable that is often around 50 dates when we consider only one level of analogy.

Then, the daily observed precipitation amount of the $N_{1}$ resulting dates provide the empirical conditional distribution considered as the probabilistic forecast for the target day.

The other most know method adds a second level of analogy on humidity variables (Table \ref{table:params_R2}). The predictor that \citet{Bontron2004} found as optimal for the France territory is a humidity index made of the multiplication of the precipitable water with the relative humidity at 850~hPa. \cite{Horton2012a} confirmed that this product is better than any other variable from the NCEP/NCAR reanalysis considered independently. When adding a second level of analogy, we subsample $N_{2}$ (30) dates in the $N_{1}$ analogues on the atmospheric circulation, to end up with a smaller number of analogue situations. When we add a second level of analogy, we keep a higher number of analogues on the first level (70 instead of 50).

@@

Predictors are generally reanalysis datasets (and outputs of a global numerical weather prediction models for the target situation in operational forecasting, which is not the topic of this paper). We will work here with the NCEP/NCAR reanalysis \citep[6-hourly, 17 atmospheric levels at a resolution of 2.5\degree, see][]{Kalnay1996}, but it can be any other reanalysis.

The predictand (which is to be predicted) is here the daily precipitation (6~a.m. to 6~a.m. the next day) measured at the MeteoSwiss' stations network, for the period 1961-2008. The time series from every available gauging station were averaged over subregions in order to smooth local effects \citep{Obled2002, Marty2012}.

@@

The calibration of the analogue method is usually done in a perfect prognosis \citep{Klein1959} framework \citep{BenDaoud2010, Bontron2004}. Perfect prognosis uses observed or reanalyzed data to calibrate the relationship between predictors and predictands. Then, when used in operational forecasting, this relationship is applied to global model forecasts, that contains larger uncertainties. This framework allow us to identify relationships that are as close as possible to the natural links between predictors and predictands, by reducing uncertainties related to numerical forecasting models. However, no model is perfect, and even reanalysis data contains a bias that cannot be ignored. For this reason, the statistical relationships identified in the perfect prognosis framework should be applied to model outputs that are as similar as possible to the model used to elaborate the reanalysis.

Another reason for working in a perfect prognosis framework is that numerical models evolve continuously, and so does the forecast they provide. Re-forecasts allows us to work on a homogeneous dataset, as they are regularly reprocessed. However, it would involve that we need to redo the calibration procedure every time a new version is available, in order to reduce the bias \citep{Wilson2002}. Moreover, the reforecasts are not re-processed for every new version of the model, meaning we still end up with a bias between the forecast and the archive. Finally, the length of reanalyses datasets are usually much longer than reforecast datasets, which allows us to identify more robust relationships. The size of the archive is indeed an important criteria for the analogue method.

@@

The accuracy of the parameters is evaluated by means of the CRPS \citep[Continuous Ranked Probability Score,][]{Brown1974, Matheson1976, Hersbach2000}. Let the precipitation variable be denoted $x$ with $x^{0}$ the observed value, and $F(x)$ the predicted cumulative distribution functions (cdf). The mean CRPS of a forecast series of length $n$ can be written:

\begin{equation}
\label{eq:CRPS}
CRPS = \frac{1}{n} \sum_{i=1}^{n} \left(  \int_{-\infty}^{+\infty} \left[ F_{i}(x)-H_{i}(x-x_{i}^{0})\right]^{2} dx \right) 
\end{equation}
where $H(x-x_{i}^{0})$ is the Heaviside function that is null when $x-x_{i}^{0}<0$, and has the value 1 otherwise.

The mean CRPS is processed on the calibration, respectively the validation periods. It means that we average the scores on all days, may they be dry, slightly rainy or with heavy precipitation. There is actually a weighting by the number: climatologically, non-rainy days are often more frequent (of course, depending on the location) and it is essential to forecast them well. The days with heavy precipitation are rare, but can instead provide individual scores ($CRPS_{j}$) very penalizing, which implies that the optimization will also try to forecast them accurately. However, these aspects are not explicitly controlled.

@@

The calibration procedure that we call ''classic'' was developed by \citet{Bontron2004} at the LTHE laborytory (INPG, Grenoble). It determines the optimal settings for the different variables of each level of analogy. The analogy levels (eg the atmospheric circulation or humidity variables) are calibrated sequentially. The procedure consists of the following steps \citet{Bontron2004}:

\begin{enumerate}
	\item Manual choice of the following parameters:
	\begin{enumerate}
		\item meteorological variable,
		\item atmospheric level,
		\item time frame (hour of observation),
		\item initial analogue numbers.
	\end{enumerate}

	\item For every level of analogy:
	\begin{enumerate}
		\item Identification of the most skilled unitary cell (1 point for humidity variables and 4 for the geopotential fields when using the S1 criteria) over a large domain. Every point (or cell) of the full domain is assessed jointly on every predictor of the level of analogy (consisting generally of the same variable, but on different atmospheric levels and at different hours).
		\item From this most skilled point, the spatial window is expanded by successive iterations in the direction of greater performance gain. The detailed stages are the followings: (i) The unitary spatial window is expanded in every 4 directions successively. The performance score is processed for these 4 windows. (ii) Only the direction providing the best improvement is applied to our spatial window. (iii) From this new spatial window, an increase in every 4 directions is once again assessed, and the best improvement is applied. (iv) The spatial window grows up by repeating the previous steps, until no improvement is reached.
		\item The number of analogues is optimized for the current level of analogy.
		\item A new level of analogy can be added, based on other variables on predefined atmospheric levels and time frames. The analogue number for the next level of analogy is initiated at a chosen value. Then, the procedure starts again from step (a). The parameters calibrated on the previous analogue levels are fixed and do not change (except the number of analogues, at the final stage). 
	\end{enumerate}
	\item Finally, the numbers of analogues are re-assessed for the different analogue levels. This is done iteratively by varying the number of analogues of each level in a systematic way.
\end{enumerate}

Calibration is done in stages, to determine the optimal parameters systematically. The steps are distinct and previously optimized parameters are generally not reassessed. \citet{Bontron2004} notes however that ''\textit{this type of algorithm, which is changing the parameters of a model in a unique path, can lead to the best solution, provided that there is no local optima}''. The advantage of this method is that it is fast, it provides acceptable results, and it has low computing requirements. We added small improvements to this method by allowing the spatial windows to do other moves, such as: (1) increase in 2 simultaneous directions, (2) decrease in 1 or 2 simultaneous directions, (3) expansion or contraction (in every direction), (4) shift of the window (without resizing) in 8 directions (including diagonals), (5) and finally all the moves described above, but with a factor of 2, 3, or more. For example, we try to increase by 2 units in one (or more) direction. This allows to skip one size that may not be optimal.

These supplementary steps often result in spatial windows that are a bit different, but the performance gain is rather marginal (gain of 0.2\%). These methods are available in the open source software AtmoSwing (Analogue Technique MOdel for Statistical Weather forecastING, www.atmoswing.org).

@@

The classic calibration is fast to optimize one spatial window for a given atmospheric level and temporal window. However, it doesn't provide an objective choice of the atmospheric level and temporal window. The only option is to try systematically every combination, which may be acceptable for no more than 2 levels. However, \citet{Horton2012a} showed that additional atmospheric levels may improve the method.

We observed during the calibration of the analogue method that the resulting parameters vary with the initial choices (such as the number of analogues). In addition, the different levels of analogy (on the atmospheric circulation and the humidity variables) are always calibrated sequentially. However, we can not exclude any dependency between them, which could lead us to select other parameters if we calibrate them together. Simultaneous calibration of all parameters has never been undertaken so far. Only a global optimization can be able to optimize all parameters of all analogy levels simultaneously.

When creating the classic calibration procedure, \citet{Bontron2004} was aware of the problem of dependencies between parameters and wrote: '' \textit{We perceive here the combinatorial aspect of our problem: variables and spatial windows are not independent. We will present our results by first searching the best variable [note: e.g. choice of the atmospheric level and the temporal window for the geopotential height] on a chosen spatial window, and next, the best window for the chosen variable. However, even by repeating the process, are we sure to have found the optimal combination?} ''. And later in his work: '' \textit{Our approach, which is again to vary the parameters one by one -- the others being fixed in a more or less arbitrary manner -- may therefore not exactly lead us to the optimal solution} ''. \citet{Bliefernicht2010} has also faced the combinatorial issue of the parameters of the analogue method and concludes that one needs to be an expert to know their respective influence, their sensitivity and their nonlinear interactions. \citet{BenDaoud2010}, when calibrating the analogue method, also stated that '' \textit{the combinatory aspect related to the calibration was found to be too high for all the parameters to be calibrated simultaneously } ''. The configuration of the analogue method resulting from a classic approach is likely to be a local optimum.

The analogue method needs to be adapted to every new region it is applied, because the leading meteorological influences are specific to this region. Even the choice of the atmospheric level and the temporal window should be reconsidered, when not the variable itself. For example, \citet{BenDaoud2010} found the vertical velocity relevant for the great plains in France, when \citet{Horton2012a} found no interest in this variable in an Alpine environment, because the vertical velocity is mainly related to the orographic effect, and was thus already well related to the atmospheric circulation itself. So, when adapting the analogue method to a new region, we should assess systematically every combination of atmospheric levels, time and spatial windows, which is an intensive task. This procedure can be automatized by a global optimization technique.

Our ambition was then to assess the feasibility of an automatic optimization of the analogue method through various techniques. The objective is to find an approach to optimize all parameters simultaneously, and thus be able to identify the global optimum in the parameter space. In addition, it can overcome the systematic manual assessments of certain parameters such as atmospheric levels and time windows. Finally, it can open new perspectives by allowing the addition of new degrees of freedom, such as a weighting of the criteria values between the atmospheric levels, and the consideration of non-overlapping spatial windows between the atmospheric levels.

\citet{Horton2012a} assessed the ability of the \citep{Nelder1965a} method based on a simplex approach. This technique didn't provide satisfying results and failed at identifying the global optimum. Indeed, the optimized parameters didn't converge and many local optimums came out. The parameters space of the analogue method is very complex and not appropriate for a linear optimization technique.

@@

Genetic algorithms (GAs) come from the world of stochastic optimization, more specifically from metaheuristic approaches. These are stochastic iterative algorithms that behave like search algorithms by exploiting the characteristics of a problem and are particularly suitable for complex parameters spaces.

Genetic algorithms are part of the family of evolutionary algorithms \citet{Back1993c, Schwefel1993}, which get inspiration from some mechanisms of biological evolution, such as reproduction, genetic mutations, chromosomal crossovers, and natural selection. GAs are the most used technique from evolutionary algorithms \citep{Back1993b}, and they are constantly improving \citep{Haupt2004}. However, with time, the different methods of evolutionary algorithms tend to be similar and share many commonalities \citep{Back1996b, Haupt2004}.

The method was developed by \citet{Holland1992b} and was popularized by \citet{Goldberg1989}. Unlike a linear or local optimization, GAs seek the global optimum on a complex surface, theoretically without restrictions, but with no guarantee to reach it.

@@

GAs mimic the evolution of a population of individuals in a new environment, by applying rules based on natural processes, such as DNA mutation, chromosomes crossover, natural selection, etc. It simulates the fact in the natural environment, the most suitable individuals tend to survive longer, to reproduce more easily, and so to influence coming generations by providing some genes that provide some good performance in a certain domain. Generation after generation, the DNA mixes and the strong genes cumulate in some individuals \citep{Beasley1996a}. Globally, the fitness of the population to its environment increases, while retaining enough variety to not converge too quickly to a local optimum.

Applications of GAs are very diversified as they can handle many parameters of various types \citep{Joines1996a}, even with very complex cost surfaces \citep{Haupt2004}. GAs work remarkably well with intervariable dependences \citep{Haupt2004}. The objective function to optimize (often named fitness function in this context) can be of different types (mathematical function, experimental or numerical modeling). Only the resulting value is used for optimization. Indeed, these algorithms do not require any knowledge of the problem, which can be used as black-box.

By means of the reproduction operator and the natural selection, the GAs focus on the most promising regions of the parameter space \citep{Holland1992b}. Points (parameters sets) are densified in these areas because the strong genes of the best individuals propagate from generation to generation.

Two conditions guarantee in theory the convergence to the global optimum \citep{Zitzler2004a}: (1) Parameters mutations that can allow to explore the entire parameter space, thus ensures that any value can be achieved with a non-zero probability. (2) A rule of elitism ensuring that an optimal solution can not be lost or damaged.

Practically, GAs allow rapidly approaching satisfactory solutions, but they do not provide the optimum solution for sure \citep{Zitzler2004a}. It is indeed mainly a matter of time. When the optimizer gets closer to the global optimum, any new improvement takes more time to appear, and the final adjustment of the parameters is very time consuming \citep{Back1993a}. For problems that require a significant amount of time in order to evaluate the objective function, as in our case, we have to limit the number of generations to get reasonable processing time. Thus, different acceptable solutions can result from one or more optimizations \citep{Holland1992b}. This is a strength and a weakness of GAs: they are very good at exploring complex parameters spaces in order to identify the most promising areas, but they will not necessarily find the best solution with the optimal values of all parameters \citep{Holland1992b}.

@@

The GAs optimize a population of individuals (parameters sets). Each individual contains a chromosome (parameters of the analogue method in our case). We call gene every parameter that constitutes the chromosome. The parameters to optimize have long been coded in binary form and assembled as strings in the canonical GAs \citep{Goldberg1989}. Encoding and decoding steps were needed to transform the variable from its floating-point representation into its binary representation, and vice versa, which introduce quantification errors \citep{Haupt2004}. According to \citet{Holland1992b}, working with binary chromosomes was supposed to be more efficient \citep{Goldberg1990a, Back1993b}. However, more and more applications use floating-point representations, allowing to avoid the coding and decoding steps and the quantification errors \citep{Haupt2004}, and which also often resulted in a performance improvement \citep{Goldberg1990a}. It is thus now considered that for continuous variables, a floating-point representation is more suited \citep{Michalewicz1996, Herrera1998a, Haupt2004, Back1996b, Gaffney2010a}.

@@

The first step of the optimization is to generate the initial population. A population is a set of $N$ individuals (each of which represents a point in the space of potential solutions, a parameters set of the analogue method in our application) that we are going to make evolve. A generation is the population at a given time.

@@

Natural selection is performed on the basis of the objective function values. The selection allows to only keep a certain part of the population, usually half ($N/2$), which can access the mating pool (intermediate generation with $N_{mp}$ members). If $N_{mp}$ is too high, the reproduction rate is too low, whereas if it is too small, the strong traits of individuals do not have the ability to accumulate in the same chromosome \citep{Haupt2004}. Several techniques exist, such as:

@@

	\item \textbf{Tournament selection}: This operator is similar to that used in natural selection, but is applied here for the successive selection of each parent. To select a parent, a number of individuals (2 or 3) are randomly picked and the best is kept. This operation is performed twice, once for each partner. This approach imitates the breeding competition in nature \citep{Haupt2004}.
\end{itemize}

@@

Once the two parents selected for breeding, they combine their chromosomes and produce two children, bringing the number of individuals in the population of $N_{mp}$ back to $N$ (the parents also return back in the total population in order to complement the next generation). The combination of chromosomes is carried out using a crossover operator, thereby generating two offspring having characteristics derived from both parents. Chromosome crossover widens the search space and favours the combination of strong genes, which can result in more suited children. It allows a mixing of genes and accumulation of positive mutations.

@@

The mutation operator is a direct modification of genes. In a binary coding, it is implemented as an inversion of one bit in a chromosome, while in real coding, it is done by changing the value of a gene. Mutations add diversity to the population and prevent a freeze of the evolution, or a genetic drift to a local optimum. Thus, it makes the convergence to the global optimum theoretically possible \citep{Beasley1993a}, as they allow exploring beyond the current region of the variable space. They therefore help prevent the algorithm to converge too quickly to a local optimum and bring new characteristics that were not present in the original population \citep{Haupt2004}.

>>>>

\abstract{The analogues method is based on a statistical relationship between synoptic atmospheric variables and local weather, which we aim at forecasting. This relationship is expressed through many parameters that are usually calibrated by means of a semi-automatic procedure. This classic calibration is relatively fast and provide acceptable results, but it has strong constraints, is made of successive steps and thus cannot handle parameters dependencies, and mainly, it cannot calibrate automatically some parameters, such as the selection of the pressure levels and the temporal windows on which the predictors are compared. In order to surpass these limitations, we assessed a global optimization technique, namely genetic algorithms, that can optimize jointly all parameters of the method and thus provide a global optimum by taking into account the parameters dependencies. Moreover, it can calibrate parameters that were previously manually assessed, and can take into account new degrees of freedom that were unthinkable before. 
These kind of optimization techniques need however to be tailored to the problem to solve. We had to assess multiple combinations of algorithms, and even to develop new operators, such as the \textit{chromosome of adaptive search radius} which was found to be very robust, in order to make recommendations for the use of genetic algorithms to optimize the analogue method. These recommendations are the primary outcome of this work, as it opens new perspective for the improvement of the analogue method, and its application to new regions or to new predictands.
We then applied the optimizer to the Rh\^{o}e catchment in the Swiss Alps and obtained coherent results which significantly improve the performance of the forecasting by analogy. The optimizer allowed us to calibrate jointly all parameters of the method and to add a weighting of the criteria per pressure level, as well as non-overlapping spatial windows.}

@@

\section{Introduction}
\label{section_intro}

The analogue method is a downscaling technique based on the idea expressed by \citet{Lorenz1969}, that similar situations in terms of atmospheric circulation are likely to lead to similar local weather \citep{Bontron2005}. It aims at forecasting a predictand, often the daily precipitation, on the basis of predictor variables describing the synoptic atmospheric circulation. Many parameters define this relationship, which are usually calibrated by means of a semi-automatic procedure.

@@

Multiple variations of the methods exist, and some aspects and parameters will not be detailed hereafter. There are mainly 2 parametrizations that are used most often: one that relies on an analogy of the atmospheric circulation, and another that adds a second level of analogy on humidity variables \citep{Obled2002, Bontron2005, Marty2012}.

The method based on the analogy of the synoptic circulation consists in the following steps (Table \ref{table:params_R1}): We assess the similarity of the atmospheric circulation of a target date with every day of the archive by processing the S1 criteria \citep[Eq.\ (\ref{eq:S1}), ][]{Teweles1954, Drosdowsky2003}, which is a comparison of gradients, over a certain spatial window. \citet{Bontron2005} showed that the geopotential height at 500~hPa and 1000~hPa are the best first predictors of the NCEP/NCAR reanalysis dataset, and that the S1 criteria performs better than scores based on absolute distances. The reason for such better results is that the S1 criteria allows comparing the circulation pattern, by means of the gradients, rather than the absolute value of the geopotential height. To cope with seasonal effects, candidate dates are extracted within a period of 4 months centred around the target date, for every year of the archive.

@@

The $N_{1}$ dates with the lowest values of S1 are considered as analogues to the target day. The number of analogues, $N_{1}$, is a parameter to calibrate. Then, the daily observed precipitation amount of the $N_{1}$ resulting dates provide the empirical conditional distribution considered as the probabilistic forecast for the target day.

The other most know parametrization adds a second level of analogy on humidity variables (Table \ref{table:params_R2}). The predictor that \citet{Bontron2004} found optimal for the France territory is a humidity index made of the product of the precipitable water with the relative humidity at 850~hPa. \cite{Horton2012a} confirmed that this index is better for the Swiss Alps than any other variable from the NCEP/NCAR reanalysis considered independently. When adding a second level of analogy, we subsample $N_{2}$ dates in the $N_{1}$ analogues on the atmospheric circulation, to end up with a smaller number of analogue situations. When we add a second level of analogy, we keep a higher number of analogues on the first level.

@@

Predictors are generally reanalysis datasets (and outputs of a global numerical weather prediction models for the target situation in operational forecasting, which is not the topic of this paper). We will work here with the NCEP/NCAR reanalysis \citep[6-hourly, 17 pressure levels at a resolution of 2.5\degree, see][]{Kalnay1996}, but it can be any other reanalysis dataset.

The predictand (which is to be predicted) is in our case the daily precipitation (6~a.m. to 6~a.m. the next day) measured at the MeteoSwiss' stations network, for the period 1961-2008. The time series from every available gauging station were averaged over subregions in order to smooth local effects \citep{Obled2002, Marty2012}.

@@

The calibration of the analogue method is usually carried out in a perfect prognosis \citep{Klein1959} framework \citep{BenDaoud2010, Bontron2004}. Perfect prognosis uses observed or reanalyzed data to calibrate the relationship between predictors and predictands. Then, when used in operational forecasting, this relationship is applied to global model forecasts, that contains larger uncertainties. This framework allow us to identify relationships that are as close as possible to the natural links between predictors and predictands, by reducing uncertainties related to numerical forecasting models. However, no model is perfect, and even reanalysis data contain a bias that cannot be ignored. For this reason, the statistical relationships identified in the perfect prognosis framework should be applied to model outputs that are as similar as possible to the model used to elaborate the reanalysis.

Another reason for working in a perfect prognosis framework is that numerical models evolve continuously, and so does the forecast they provide. Re-forecasts would allow us to work on a homogeneous dataset, as they are regularly reprocessed. However, we would need to redo the calibration procedure every time a new version is available, in order to reduce the bias \citep{Wilson2002}. Moreover, the reforecasts are not re-processed for every new version of the model, meaning we still end up with a bias between the forecast and the archive. Finally, the length of reanalyses datasets are usually much longer than reforecast datasets, which allows us to identify more robust relationships. The size of the archive is indeed an important criteria for the analogue method.

@@

The accuracy of the parameters is evaluated by means of the CRPS \citep[Continuous Ranked Probability Score,][]{Brown1974, Matheson1976, Hersbach2000}. It allows assessing the predicted cumulative distribution functions $F(y)$ compared to the observed value $y^{0}$. The better the forecast, the smaller the score. The mean CRPS of a forecast series of length $n$ can be written:

\begin{equation}
\label{eq:CRPS}
CRPS = \frac{1}{n} \sum_{i=1}^{n} \left(  \int_{-\infty}^{+\infty} \left[ F_{i}(y)-H_{i}(y-y_{i}^{0})\right]^{2} dy \right) 
\end{equation}
where $H(y-y_{i}^{0})$ is the Heaviside function that is null when $y-y_{i}^{0}<0$, and has the value 1 otherwise. The mean CRPS is averaged on the calibration, respectively the validation periods, on all days, may they be dry, slightly rainy or with heavy precipitation.

This score is now commonly used for the evaluation of continuous variables prediction systems \citep{Casati2008, Marty2010}. To compare the value of the score in regard to a reference, we often consider its skill score value, and use the climatological distribution as the reference. The CRPSS (\textit{Continuous Ranked Probability Skill Score}) is thus defined as following:

\begin{equation}
\label{eq:CRPSS}
CRPSS = \dfrac{CRPS-CRPS_{r}}{CRPS_{p}-CRPS_{r}} = 1-\dfrac{CRPS}{CRPS_{r}}
\end{equation}
where $CRPS_{r}$ is the CRPS value for the reference and $CRPS_{p}$ would be the one for a perfect forecast ($CRPS_{p} = 0$).

@@

The calibration procedure that we call ''classic'' was developed by \citet{Bontron2004} at the LTHE laboratory (INPG, Grenoble). It determines the optimal parameters for the different variables of each level of analogy. The analogy levels (eg the atmospheric circulation or humidity index) are calibrated sequentially. The procedure consists of the following steps \citep{Bontron2004}:

\begin{enumerate}
	\item Manual selection of the following parameters:
	\begin{enumerate}
		\item meteorological variable,
		\item pressure level,
		\item temporal window (hour of observation),
		\item initial analogue numbers.
	\end{enumerate}

	\item For every level of analogy:
	\begin{enumerate}
		\item Identification of the most skilled unitary cell (1 point for humidity variables and 4 for the geopotential height when using the S1 criteria) over a large domain. Every point (or cell) of the full domain is assessed jointly on all predictors of the level of analogy (consisting generally of the same variable, but on different pressure levels and at different hours).
		\item From this most skilled point, the spatial window is expanded by successive iterations in the direction of greater performance gain. The detailed stages are the followings: (i) The unitary spatial window is expanded in every 4 directions successively. The performance score is processed for these 4 windows. (ii) Only the direction providing the best improvement is applied to our spatial window. (iii) From this new spatial window, an increase in every 4 directions is once again assessed, and the best improvement is applied. (iv) The spatial window grows up by repeating the previous steps, until no improvement is reached.
		\item The number of analogues is optimized for the current level of analogy.
		\item A new level of analogy can be added, based on other variables (such as the humidity index) on predefined pressure levels and time frames. The number of analogues for the next level of analogy is initiated at a chosen value. Then, the procedure starts again from step (a) for the new level. The parameters calibrated on the previous analogue levels are fixed and do not change (except the number of analogues, at the final stage). 
	\end{enumerate}
	\item Finally, the numbers of analogues are re-assessed for the different levels of analogy. This is done iteratively by varying the number of analogues of each level in a systematic way.
\end{enumerate}

The calibration is thus done in successive steps. Previously calibrated parameters are generally not reassessed. The advantage of this method is that it is fast, it provides acceptable results, and it has low computing requirements. We added small improvements to this method by allowing the spatial windows to do other moves, such as: (1) increase in 2 simultaneous directions, (2) decrease in 1 or 2 simultaneous directions, (3) expansion or contraction (in every direction), (4) shift of the window (without resizing) in 8 directions (including diagonals), and finally (5) all the moves described above, but with a factor of 2, 3, or more. For example, we try to increase by 2 units in one (or more) direction. This allows to skip one size that may not be optimal.

These supplementary steps often result in spatial windows that are a bit different, but the performance gain is rather marginal. These methods are available in the open source software AtmoSwing (Analogue Technique MOdel for Statistical Weather forecastING, www.atmoswing.org).

@@

The classic calibration is fast to optimize one spatial window for a given pressure level and temporal window. However, it doesn't provide an objective selection of the pressure level and temporal window. The only option is to try systematically every combination, which may be acceptable for no more than 2 levels. However, \citet{Horton2012a} showed that additional pressure levels may improve the method.

We observed during the calibration of the analogue method that the resulting parameters vary with the initial choices (such as the number of analogues). In addition, the different levels of analogy (eg on the atmospheric circulation and the humidity index) are always calibrated sequentially. However, we can not exclude any dependency between them, which could lead us to select another parametrization if we calibrate them together. Simultaneous calibration of all parameters has never been undertaken so far. Only a global optimization technique can be able to optimize all parameters of all analogy levels simultaneously.

When creating the classic calibration procedure, \citet{Bontron2004} was aware of the problem of dependencies between parameters and wrote: '' \textit{We perceive here the combinatorial aspect of our problem: variables and spatial windows are not independent. We will present our results by first searching the best variable [note: e.g. selection of the pressure level and the temporal window for the geopotential height] on a chosen spatial window, and next, the best window for the chosen variable. However, even by repeating the process, are we sure to obtain the optimal combination?} ''. And later in his work: '' \textit{Our approach, which is again to vary the parameters one by one -- the others being fixed in a more or less arbitrary manner -- may therefore not exactly lead us to the optimal solution} ''. \citet{Bliefernicht2010} has also faced the combinatorial issue of the parameters of the analogue method and concludes that one needs to be an expert to know their respective influence, their sensitivity and their nonlinear interactions. \citet{BenDaoud2010}, when calibrating the analogue method, also stated that '' \textit{the combinatory aspect related to the calibration was found to be too high for all the parameters to be calibrated simultaneously } ''.

The analogue method needs to be adapted to every new region it is applied, because the leading meteorological influences are specific to this region. Even the selection of the pressure level and the temporal window should be reconsidered, when not the variable itself. For example, \citet{BenDaoud2010} found the vertical velocity relevant for the great plains in France, when \citet{Horton2012a} found no interest in this variable in an Alpine environment, because in the Alps, the vertical motion is mainly controlled by orographic effects, and was thus already well related to the atmospheric circulation itself. So, when adapting the analogue method to a new region, we should assess systematically every combination of pressure levels, time and spatial windows, which is an intensive task. This procedure can be automatized by a global optimization technique.

Our ambition was then to assess the feasibility of an automatic optimization of the analogue method through various techniques. The objective was to find an approach to optimize all parameters simultaneously, and thus be able to identify the global optimum in the parameter space. In addition, it can overcome the systematic manual assessments of certain parameters such as the selection of the pressure levels and time windows. Finally, it can open new perspectives by allowing the addition of new degrees of freedom, such as a weighting of the criteria values between the pressure levels, and the consideration of non-overlapping spatial windows between the pressure levels.

\citet{Horton2012a} assessed the ability of the \citet{Nelder1965a} method based on a simplex approach. This technique didn't provide satisfying results and failed at identifying the global optimum. Indeed, the results didn't converge and many local optimums came out. The parameter space of the analogue method is very complex and not appropriate for a linear optimization technique. Genetic algorithms were found to be much more relevant for such application.

@@

Genetic algorithms (GAs) come from the world of stochastic optimization, more specifically from metaheuristic approaches. These are stochastic iterative algorithms that behave like search algorithms by exploiting the characteristics of a problem and are particularly suitable for complex parameter spaces.

Genetic algorithms are part of the family of evolutionary algorithms \citep{Back1993b, Schwefel1993}, which get inspiration from some mechanisms of biological evolution, such as reproduction, genetic mutations, chromosomal crossovers, and natural selection. GAs are the most used technique from evolutionary algorithms \citep{Back1993b}, and they are constantly improving \citep{Haupt2004}. However, with time, the different methods of evolutionary algorithms tend to be similar and share many commonalities \citep{Back1996b, Haupt2004}.

The method was originally developed by \citet{Holland1992b} and popularized by \citet{Goldberg1989}. Unlike a linear or local optimization, GAs seek the global optimum on a complex surface, theoretically without restriction, but with no guarantee to reach it.

@@

GAs mimic the evolution of a population of individuals in a new environment, by applying rules based on natural processes, such as DNA mutation, chromosomes crossover, natural selection, etc. It simulates the fact that in a natural environment, the most suitable individuals tend to survive longer, to reproduce more easily, and so to influence coming generations by providing genes that provide some good performance in a certain domain. Generation after generation, the DNA mixes and the strong genes cumulate in some individuals \citep{Beasley1996a}. Globally, the fitness of the population to its environment increases, while retaining enough variety to not converge too quickly to a local optimum.

Applications of GAs are very diversified as they can handle many parameters of various types \citep{Joines1996a}, even with very complex cost surfaces \citep{Haupt2004}. GAs work remarkably well with intervariable dependences \citep{Haupt2004}. The objective function to optimize (often named fitness function in this context) can be of different types (mathematical function, experimental or numerical modeling). Only the resulting value is used for optimization. Indeed, these algorithms do not require any knowledge of the problem, which can be used as black-box, but they must be adapted in order to perform optimally.

By means of the reproduction operator and the natural selection, the GAs focus on the most promising regions of the parameter space \citep{Holland1992b}. Points (parameter sets) are densified in these areas because the strong genes of the best individuals propagate from generation to generation.

Two conditions guarantee in theory the convergence to the global optimum \citep{Zitzler2004a}: (1) Parameters mutations that can allow to explore the entire parameter space, thereby ensures that any value can be achieved with a non-zero probability. (2) A rule of elitism ensuring that an optimal solution cannot be lost or damaged.

Practically, GAs allow rapidly approaching satisfactory solutions, but they do not provide the optimum solution for sure \citep{Zitzler2004a}. It is indeed mainly a matter of time. When the optimizer gets closer to the global optimum, any new improvement takes more time to appear (see figure \ref{fig:evolution}), and the final adjustment of the parameters is very time consuming \citep{Back1993a}. For problems that require a significant amount of time in order to evaluate the objective function, as in our case, we have to limit the number of generations to get reasonable processing time. Thus, different acceptable solutions can result from one or more optimizations \citep{Holland1992b}. This is a strength and a weakness of GAs: they are very good at exploring complex parameter spaces in order to identify the most promising areas, but they will not necessarily find the best solution with the optimal values of all parameters \citep{Holland1992b}.

@@

The GAs optimize a population of individuals (parameter sets). Each individual contains a chromosome (parameters of the analogue method in our case). We call gene every parameter that constitutes the chromosome. The parameters to optimize have long been coded in binary form and assembled as strings in the canonical GAs \citep{Goldberg1989}. Encoding and decoding steps were needed to transform the variable from its floating-point representation into its binary representation, and vice versa, which introduce quantification errors \citep{Haupt2004}. According to \citet{Holland1992b}, working with binary chromosomes was supposed to be more efficient \citep{Goldberg1990a, Back1993b}. However, more and more applications use floating-point representations, allowing to avoid the coding and decoding steps and the quantification errors \citep{Haupt2004}, and which also often resulted in a performance improvement \citep{Goldberg1990a}. It is thus now considered that for continuous variables, a floating-point representation is more suited \citep{Michalewicz1996, Herrera1998a, Haupt2004, Back1996b, Gaffney2010a}.

@@

The first step of the optimization is to generate the initial population. A population is a set of $N$ individuals (each of which represents a point in the space of potential solutions, a parameter set of the analogue method in our application) that we are going to make evolve. A generation is the population at a given time.

@@

Natural selection is performed on the basis of the values of the objective function. The selection allows to only keep a certain part of the population, usually half ($N/2$), which can access the mating pool (intermediate generation with $N_{mp}$ members). If $N_{mp}$ is too high, the reproduction rate is too low, whereas if it is too small, the strong traits of individuals do not have the ability to accumulate in the same chromosome \citep{Haupt2004}. Several techniques exist, such as:

@@

	\item \textbf{Tournament selection}: This operator is similar to the one used in natural selection, but is applied here for the successive selection of each parent. To select a parent, a number of individuals (2 or 3) are randomly picked and the best is kept. This operation is performed twice, once for each partner. This approach imitates the breeding competition in nature \citep{Haupt2004}.
\end{itemize}

@@

Once the two parents are selected for breeding, they combine their chromosomes and produce two children, bringing the number of individuals in the population back to $N$ (the parents also return back in the total population in order to complement the next generation). The combination of chromosomes is carried out using a crossover operator, thereby generating two offspring having characteristics derived from both parents. Chromosome crossover widens the search space and favours the combination of strong genes, which can result in more suited children. It allows a mixing of genes and accumulation of positive mutations.

@@

The mutation operator is a direct modification of genes. In a binary coding, it is implemented as an inversion of some bits in a chromosome, while in real coding, it is done by changing the gene values. Mutations add diversity to the population and prevent a freeze of the evolution, or a genetic drift to a local optimum. Thus, it makes the convergence to the global optimum theoretically possible \citep{Beasley1993a}, as they allow exploring beyond the current region of the parameter space. They therefore help preventing the algorithm to converge too quickly to a local optimum and bring new characteristics that were not present in the original population \citep{Haupt2004}.
